raptr: Representative and Adequate Prioritisation Toolkit in R

### 2016-07-22 code/rmarkdown/article.Rmd
+ article fixes + readme updates

2. To address this issue, we developed the \\texttt{raptr: Representative and Adequate Prioritisation Toolkit in R}, a toolkit to guide reserve selection using explicit targets for representing biodiversity processes as well as area protection targets. Users set \"space targets\" to secure a representative sample of each feature within an attribute space that reflects a biodiversity process (eg. an attribute space expressing variation in genetic characteristics between individuals in an area, or variation in climatic conditions between inhabited areas). We explored the functionality of this package using a simulated study and two case studies. In each study, we generated solutions that secured a proportion of the species' distributions using amount targets--representing conventional reserve selection--and compared them with solutions generated using both amount and space targets.

@@

# Introduction
<!-- conservation and reserve networks -->
Perhaps the most fundamental aim of conservation is to maximise the long-term persistence of biodiversity at organisational levels [@r423; @r255]. To achieve this, conservation actions must preserve biodiversity patterns (eg. populations, species, ecosystems), but also crucially the processes that sustain them. One of the major tangible achievements of modern conservation has been the act of setting aside areas for preservation [@r440]. Reserve networks buffer species from gross threatening processes and set the stage for enhanced management interventions [@r465]. However, the resources available for conservation action are limited, and so reserve networks must be sited in places that satisfy conservation objectives for minimum cost [@r255]. To achieve this, reserve selection is often formulated as an optimisation problem and then solved to identify cost-effective candidate reserve systems [termed prioritisations; @r255]. Many decision support tools have been developed to help identify cost-effective solutions [eg. \texttt{ ConsNet}, @r446; \texttt{ Marxan}, @r22; \texttt{ Zonation}, @r429]. Typically, these tools are used to deliver a prioritisation that preserves a set of species of interest to the conservation planner (termed target species or features). Given a set of species, decision makers can use these tools to preserve biodiversity patterns by generating a prioritisation that secures an adequate proportion of each species' range.

<!-- biodiversity processes are important -->
However, to achieve effective conservation, reserve networks must do more than cover enough area. They must capture the processes that sustain biodiversity over the long term; they must capture both ecological and evolutionary processes [@r3; @r255]. Ecological processes, such as predator-prey interactions, pollination, and decomposition, are required for biodiversity to persist over short time-scales. Typically, they operate over small geographic domains--with exceptions such as migration and refugial habitats--and can be preserved using suitably large planning units [@r446] that each contain a discrete unit of habitat [@r448]. On the other hand, evolutionary processes are required for biodiversity to persist over long time-scales, and they typically operate over large geographic domains. Protected areas must represent adaptive evolutionary processes to foster resilience against environmental change [eg. climate change; @r247]. Protected areas must also preserve neutral evolutionary processes [@r5; @r67; @r63], arising from restriction of gene flow between populations. They are important for maintaining genetic diversity, and avoiding inbreeding depression. In recent decades, a wealth of data relevant to evolutionary processes has become available to conservation planners [eg. bioclimatic, genetic, and trait data; @r33; @r453; @r460]. Yet such data are rarely used to guide conservation planning [@r61]. This is perhaps in large part due to that fact that existing reserve selection tools focus on capturing either biodiversity patterns or processes--but not both.

<!-- parametrisation of biodiversity patterns and processes in conventional conservation planning tools -->
Existing conservation planning tools are generally not well-suited for representing biodiversity processes [but see @r203]. To preserve biodiversity processes, a prioritisation must capture a representative sample of each species. For instance, to preserve predator-prey interactions, a prioritisation must preserve individuals from each predator and prey species in the same area. To preserve adaptive evolutionary processes, a prioritisation must preserve the adaptive landscape of each species--populations experiencing different selection pressures [@r63]. To preserve neutral evolutionary processes, a prioritisation must secure individuals descended from each of the genetic lineages that comprise each species [@r5]. Previous attempts to accommodate such into multi-species conservation planning have partitioned species' ranges into different groups, for example at habitat discontinuities [e.g. @r2] as a pre-processing step to render a new set of "pseudo-species". However, this approach assumes that the biodiversity processes that operate across a species' range can be readily split into discrete units. Yet data on biodiversity processes is often continuous and hyper-dimensional, and often cannot be reduced to a few categories without significant information loss [@r218].

>>>>

2. To address this issue, we developed the \\texttt{raptr: Representative and Adequate Prioritisation Toolkit in R} to guide reserve selection using explicit targets for representing biodiversity processes as well as area protection targets. Users set \"space targets\" to secure a representative sample of each feature within an attribute space that reflects a biodiversity process (eg. an attribute space expressing variation in genetic characteristics between individuals in an area, or variation in climatic conditions between inhabited areas). We explored the functionality of this package using a simulated study and two case studies. In each study, we generated solutions that secured a proportion of the species' distributions using amount targets--representing conventional reserve selection--and compared them with solutions generated using both amount and space targets.

@@

# Introduction
<!-- conservation and reserve networks -->
Perhaps the most fundamental aim of conservation is to maximise the long-term persistence of biodiversity [@r423; @r255]. To achieve this, conservation actions must preserve biodiversity patterns (eg. populations, species, ecosystems), but also crucially the processes that sustain them. One of the major tangible achievements of modern conservation has been the act of setting aside areas for preservation [@r440]. Reserve networks buffer species from gross threatening processes and set the stage for enhanced management interventions [@r465]. However, the resources available for conservation action are limited, and so reserve networks must be sited in places that satisfy conservation objectives for minimal cost [@r255]. To achieve this, reserve selection is often formulated as an optimisation problem and then solved to identify cost-effective candidate reserve systems [termed prioritisations; @r255]. Many decision support tools have been developed to help identify cost-effective solutions [eg. \texttt{ ConsNet}, @r446; \texttt{ Marxan}, @r22; \texttt{ Zonation}, @r429]. Typically, these tools are used to deliver a prioritisation that secures a set of species of interest to the conservation planner (termed target species or features). Given a set of species, decision makers can use these tools to preserve biodiversity patterns by generating a prioritisation that secures an adequate proportion of each species' range. However, to achieve effective conservation, reserve networks must do more than cover enough area.

<!-- biodiversity processes are important -->
Prioritisations must capture the ecological and evolutionary processes that sustain biodiversity [@r3; @r255]. Ecological processes, such as predator-prey interactions, pollination, and decomposition, are required for biodiversity to persist over short time-scales. Typically, they operate over small geographic domains--with exceptions such as migration and refugial habitats--and can be preserved using suitably large planning units [@r446] that each contain a discrete unit of habitat [@r448]. On the other hand, evolutionary processes are required for biodiversity to persist over long time-scales, and they typically operate over large geographic domains. Protected areas must represent adaptive evolutionary processes to foster resilience against environmental change [eg. climate change; @r247]. Protected areas must also preserve neutral evolutionary processes [@r5; @r67; @r63], arising from restriction of gene flow between populations. They are important for maintaining genetic diversity, and avoiding inbreeding depression. In recent decades, a wealth of data relevant to evolutionary processes has become available to conservation planners [eg. bioclimatic, genetic, and trait data; @r33; @r453; @r460]. Yet such data are rarely used to guide conservation planning [@r61]. This is perhaps in large part due to the fact that existing reserve selection tools focus on capturing either biodiversity patterns or processes--but not both.

<!-- parametrisation of biodiversity patterns and processes in conventional conservation planning tools -->
Existing conservation planning tools are generally not well-suited for representing biodiversity patterns and processes. To preserve biodiversity processes, a prioritisation must capture a representative sample of each species. For instance, to preserve predator-prey interactions, a prioritisation must preserve individuals from each predator and prey species in the same area. To preserve adaptive evolutionary processes, a prioritisation must preserve the adaptive landscape of each species--populations experiencing different selection pressures [@r63]. To preserve neutral evolutionary processes, a prioritisation must secure individuals descended from each of the genetic lineages that comprise each species [@r5]. Planning tools that focus on such biodiversity processes [eg. \texttt{Diversity}; @r203] are unable to accomodate species-specific targets to ensure that prioritisations secure biodiversity features. Similarly, planning tools that focus on biodiversity patterns [eg. \texttt{Marxan}] cannot easily accomodate biodiversity processes. Previous attempts to accommodate processes into multi-species conservation planning have partitioned species' ranges into different groups, for example at habitat discontinuities [e.g. @r2] as a pre-processing step to render a new set of "pseudo-species". However, this approach assumes that the biodiversity processes that operate across a species' range can be readily split into discrete units. Yet data on biodiversity processes is often continuous, hierarchical, and hyper-dimensional, and so often cannot be reduced to a few categories without significant information loss [@r218].
